RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-15 main.tex
:pencil: Add descriptions for scattering applications

		Due to double modulation, the primary equivalent channel is a function of \emph{coded} backscatter symbols
			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},

@@

		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of RIScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is

@@

		Besides, we define the total received energy per backscatter block as $z=\sum_{n \in \mathcal{N}} \lvert y[n] \rvert^2$.

@@

		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/discrete_outputs.tex}
			}
			\caption{The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space, and each decision region consists of at least one neighbor energy bins.}
			\label{fi:discrete_outputs}
		\end{figure}
		As shown in Fig. \ref{fi:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can group adjacent high-resolution energy bins for backscatter decision regions.
		Thus, problem \eqref{op:decision_threshold} is recast as
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
			\addConstraint{\eqref{co:sequential_threshold},}
		\end{maxi!}
		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmc}.
		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
		In Section \ref{se:simulation_results}, both schemes will be compared with the \gls{ml} thresholding \cite{Qian2019}
		\begin{equation}
			t_{l}^{\mathrm{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
			\label{eq:detection_threshold_maximum_likelihood}
		\end{equation}
		which is generally suboptimal for problem \eqref{op:decision_threshold} except when all nodes are with equiprobable inputs.
	\end{subsection}
\end{section}

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig. \ref{fi:riscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=7$ and $\varepsilon=\num{1e-3}$.
	All achievable rate curves/regions are averaged over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.

	\begin{subsection}{Evaluation of Algorithms}
		\begin{subsubsection}{Initialization}
			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing the primary priority $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
			At $\rho=0$ where backscatter performance is absolutely prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k \in \mathcal{K}} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
			At the following points, both algorithms are initialized by the solutions of the previous point.
		\end{subsubsection}

@@

			In Fig. \ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration at $\rho=0$.
			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations based on \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be evaluated by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
			The \gls{bcd} algorithm typically takes around \num{5} iterations to converge.
			At the following points (not shown here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate gains for the RIScatter system.
		\end{subsubsection}
	\end{subsection}

@@

		% AmBC: co-located non-cooperative receivers, use SINR to evaluate primary rate even if backscatter symbols are not Gaussian distributed
		% For a fair comparison, we employ energy-based backscatter detection for scattering applications evaluated in this subsection.
		% For a fair comparison, we evaluate different scattering applications with backscatter energy detection over the setup in Fig. \ref{fi:riscatter_network}.
		For a fair comparison, we employ backscatter energy detection for these scattering applications over the setup in Fig. \ref{fi:riscatter_network}:
		% employ energy-based backscatter detection for scattering applications evaluated in this subsection.

@@

			% The \gls{ap} becomes carrier emitter and the user becomes backscatter reader.

@@

				y^{\text{\gls{bbc}}}[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} + v[n],

@@

			% which follows non-zero mean complex Gaussian distribution $y_{m_{\mathcal{K}}}^{\text{BBC}}[n] \sim \mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
			% The corresponding \gls{pdf} of receive energy over $N$ primary blocks is

@@

				f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}})^{N-1} \exp(-(z-\mu_{m_{\mathcal{K}}})/\sigma_v^2)}{\sigma_v^{2N} (N-1)!},

@@

			where $\mu_{m_{\mathcal{K}}} \triangleq N \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2$.

@@

			% Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the interference from finite-input backscatter sources by those from independent Gaussian sources.}

@@

				I_P^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\mathrm{D}}^H\boldsymbol{w}\rvert^2}{\lvert\sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),

@@

			while the total backscatter rate is given by \eqref{eq:backscatter_mutual_information} with equiprobable inputs.
			\item \emph{\gls{sr}:} When $N$ is sufficiently large, the primary ergodic rate can be approximated by \eqref{eq:primary_mutual_information} with equiprobable inputs.
			The intermediate signal after perfect \gls{sic} is \cite{Long2020a}

@@

				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n] + v[n],

@@

			which follows \gls{cscg} distribution $\mathcal{CN}\bigl(0,\hat{\sigma}_{m_{\mathcal{K}}}^2\bigr)$ with $\hat{\sigma}_{m_{\mathcal{K}}}^2 \triangleq \lvert\sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
			The corresponding \gls{pdf} of intermediate energy over $N$ primary blocks is

@@

				f^{\text{\gls{sr}}}(\hat{z}|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{\hat{z}^{N-1} \exp(-\hat{z}/\hat{\sigma}_{m_{\mathcal{K}}}^2)}{\hat{\sigma}_{m_{\mathcal{K}}}^{2N} (N-1)!},

@@

		\begin{subsubsection}{Decision Threshold}
			We compare the following decision thresholds for problem \eqref{op:decision_threshold_discrete}:
			\begin{itemize}
				\item \emph{\gls{dp}:} Benchmark \gls{dp} method for sequential quantizer \cite{He2021};
				\item \emph{\gls{smawk}:} \emph{\gls{dp}} accelerated by the \gls{smawk} algorithm \cite{He2021};
				\item \emph{Bisection:} The traverse-then-bisect algorithm \cite{Nguyen2020a};
				\item \emph{\gls{ml}:} Maximum likelihood detector \eqref{eq:detection_threshold_maximum_likelihood} \cite{Qian2019}.
			\end{itemize}

>>>>

		Due to double modulation, the primary equivalent channel is a function of \emph{coded} backscatter symbols\footnote{Expression \eqref{eq:equivalent_channel_bc} is often used in \gls{bc} literatures while expression \eqref{eq:equivalent_channel_ris} is commonly observed in \gls{ris} literatures.}
		% \begin{equation}
		% 	\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \overset{\text{(a)}}{=} \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \overset{\text{(b)}}{=} \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
		% 	\label{eq:equivalent_channel}
		% \end{equation}
				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \label{eq:equivalent_channel_bc}                    \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}, \label{eq:equivalent_channel_ris}

@@

		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of RIScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
		The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is

@@

		Besides, we define the total received energy per backscatter block as $z=\sum_{n \in \mathcal{N}} \bigl\lvert y[n] \bigr\rvert^2$.

@@

		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/discrete_outputs.tex}
			}
			\caption{The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space, and each decision region consists of at least one neighbor energy bins.}
			\label{fi:discrete_outputs}
		\end{figure}
		As shown in Fig. \ref{fi:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can group adjacent high-resolution energy bins for backscatter decision regions.
		Thus, problem \eqref{op:decision_threshold} is recast as
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
			\addConstraint{\eqref{co:sequential_threshold},}
		\end{maxi!}
		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmc}.
		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
		In Section \ref{se:simulation_results}, both schemes will be compared with the \gls{ml} thresholding \cite{Qian2019}
		\begin{equation}
			t_{l}^{\text{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
			\label{eq:detection_threshold_ml}
		\end{equation}
		which is generally suboptimal for problem \eqref{op:decision_threshold} except when all nodes are with equiprobable inputs.
	\end{subsection}
\end{section}

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig. \ref{fi:riscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=9$ and $\varepsilon=\num{1e-3}$.
	All achievable rate curves/regions are averaged over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.

	\begin{subsection}{Evaluation of Proposed Algorithms}
		\begin{subsubsection}{Initialization}
			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing the primary priority $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
			At $\rho=0$ where backscatter performance is absolutely prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
			At the following points, both algorithms are initialized by the final solutions at the previous point.
		\end{subsubsection}

@@

			In Fig. \ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration.
			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations of closed-form expression \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be evaluated by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
			In comparison, the \gls{bcd} algorithm typically requires no more than \num{5} iterations to converge.
			At the following points (not shown here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate benefits for the RIScatter system.
		\end{subsubsection}
	\end{subsection}

@@

		For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:

@@

@@

				% y^{\text{\gls{bbc}}}[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} + v[n],
				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k\Bigr) \boldsymbol{w} + v[n],

@@

			% which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
			% \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k

@@

				f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
				\label{eq:energy_distribution_bbc}

@@

			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2$.
			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{bbc}}} \triangleq N \bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr) \boldsymbol{w} \bigr\rvert^2$.
			The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,
				t_l^{\text{\gls{bbc}}} = \frac{\mu_{l-1}^{\text{\gls{bbc}}} \exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{bbc}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{bbc}}}-\mu_{l}^{\text{\gls{bbc}}})/\sigma_v^2 (N-1)\bigr) - 1}.
				\label{eq:detection_threshold_ml_bbc}

@@

@@

				I_P^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\mathrm{D}}^H\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),

@@

			while the total backscatter rate follows \eqref{eq:backscatter_mutual_information} with uniform input distribution.
			\item \emph{\gls{sr}:} When $N$ is sufficiently large, the primary ergodic rate under semi-coherent detection can be approximated by \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal used for backscatter detection is

@@

				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n] + v[n],

@@

			which, under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$, is only subject to the noise uncertainty and follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \boldsymbol{w} s[n],\sigma_v^2\bigr)$.
			By the law of large numbers, as $N$ goes to infinity, the \gls{pdf} of accumulated intermediate energy approaches

@@

				f^{\text{\gls{sr}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
				\label{eq:energy_distribution_sr}
			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}} \triangleq N \bigl\lvert \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w} \bigr\rvert^2$. The \gls{ml} decision threshold is, $\forall l \in \mathcal{L} \setminus \{L\}$,
				t_l^{\text{\gls{sr}}} = \frac{\mu_{l-1}^{\text{\gls{sr}}} \exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{sr}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - 1}.
				\label{eq:detection_threshold_ml_sr}

@@

		\begin{subsubsection}{Decision Threshold}
			We compare the following decision thresholds for problem \eqref{op:decision_threshold_discrete}:
			\begin{itemize}
				\item \emph{\gls{dp}:} Benchmark \gls{dp} method for sequential quantizer \cite{He2021};
				\item \emph{\gls{smawk}:} \emph{\gls{dp}} accelerated by the \gls{smawk} algorithm \cite{He2021};
				\item \emph{Bisection:} The traverse-then-bisect algorithm \cite{Nguyen2020a};
				\item \emph{\gls{ml}:} Maximum likelihood detector \eqref{eq:detection_threshold_ml} \cite{Qian2019}.
			\end{itemize}
